\\documentclass{article}
\\usepackage[margin=1in]{geometry}
\\usepackage{enumitem}
\\begin{document}

\\section*{QLDPCWatch Implementation Status}

Last updated: 2026-03-17

\\subsection*{Completed}
\\begin{itemize}[leftmargin=*]
  \\item Project scaffold, package metadata, and CLI entrypoint.
  \\item arXiv client with API rate limiting (\\textgreater{}=3s/request) and retries.
  \\item SQLite state DB for runs, paper versions, and hash-based idempotency.
  \\item Structured extraction schema (PaperExtraction) and strict validation.
  \\item OpenAI Responses API integration for JSON-schema extraction.
  \\item Per-paper artifacts: metadata, extraction, summary, bibtex, changelog.
  \\item Global indexes (JSON/CSV), weekly digests, local search, version diffs.
  \\item Static site generation under \\texttt{/site/}.
  \\item GitHub Actions scheduled/manual update workflow.
  \\item Unit tests for parser, DB state, and schema validation.
  \\item Formatter/linter/tests executed successfully (\\texttt{ruff}, \\texttt{pytest}).
  \\item End-to-end smoke update run completed; paper folders/index/digest/site generated.
  \\item Default arXiv retrieval updated to abstract-targeted (\\texttt{abs:}) quantum-LDPC decoder queries.
  \\item Added \\texttt{qldpcwatch update --refresh-fallback} to re-extract existing fallback entries.
  \\item Added \\texttt{qldpcwatch report} to emit cross-paper decoder/error-model/performance/repo reports.
  \\item Full-corpus update run executed on 155 papers; index/digest/site and per-paper metadata refreshed.
  \\item Added fail-fast guard: \\texttt{--refresh-fallback} now requires \\texttt{OPENAI\\_API\\_KEY}.
  \\item Fixed OpenAI strict schema compatibility by forcing all object properties into \\texttt{required} (resolves 400 \\texttt{invalid\\_json\\_schema} errors).
  \\item Manually added a full-text-backed review entry for \\texttt{2603.05481v1} (``High-performance syndrome extraction circuits for quantum codes'') and refreshed the repo artifacts needed to track it.
\\end{itemize}

\\subsection*{In Progress}
\\begin{itemize}[leftmargin=*]
  \\item Routine updates and future paper refresh runs.
  \\item Full-detail corpus re-extraction with PDFs + valid OpenAI key (current corpus remains fallback-only: 155/155).
\\end{itemize}

\\subsection*{Completed (Deployment)}
\\begin{itemize}[leftmargin=*]
  \\item Initialized git history in small logical commits.
  \\item Created GitHub repository \\texttt{aleverrier/decoders-review}.
  \\item Connected local \\texttt{origin} to \\texttt{git@github.com:aleverrier/decoders-review.git}.
  \\item Pushed \\texttt{main} and enabled branch tracking (\\texttt{main...origin/main}).
\\end{itemize}

\\subsection*{Pending}
\\begin{itemize}[leftmargin=*]
  \\item Re-run full fallback refresh with a valid OpenAI key loaded in the same shell.
\\end{itemize}

\\end{document}
